MONID

### 2023-09-11 Presentation/presentation.tex
update

>>>>

\section{Introduction}

\setLayout{mainpoint}
\setBGColor{DarkPurple}
\begin{frame}{}
    \frametitle{Introduction}
\end{frame}
\setLayout{vertical}

\begin{frame}
    \frametitle{What is MONID?}
    MONID is a prototype which can detect intrusions on a system; in this scenario we are focusing on a \textit{signature-based} approach.\\
    \vspace{5mm}
    In order:
    \begin{enumerate}
        \item we will use the logic EAGLE to define intrusion patterns using temporal logic formula $\varphi$; in this case the monitored formula will be $\psi=\square (\neg\varphi)$.
        \item MONID will create a stream of events $\sigma=\alpha_{1},\alpha_{2},\ldots$ obtained from a merge of the logs by ascending time order;
        \item a monitor will processes each event $\alpha_i$ as it happens and updates the monitored formula $\psi$ to store a relevant summary;
        \item an intrusion alarm is triggered if, for any reason, $\alpha_{1},\alpha_{2} \ldots\not\models\psi$.
    \end{enumerate}

\end{frame}

\begin{frame}
    \frametitle{What is MONID? (cont'd)}
    The architecture is the following.\\
    \vspace{5mm}
    \includegraphics[scale=0.25]{images/monid.png}
\end{frame}
